Supplemental information

### 2017-10-27 manuscript/supplemental.tex
spellcheck, all sections now included?

      Barbour \emph{et al.} sampled 145 branches from 
      \emph{Salix hookeriana} of 26 genotypes. They recorded galls 
      made by four species of Cecidomyid midges on each branch. We 
      transformed these data to a binary genotype-galler network 
      matrix, where an entry $ij$ was 1 if galler $i$ was observed 
      on any branch of genotype $j$ and 0 otherwise. In total, this 
      network contained 75 realized galler-genotype interactions 
      out of a potential 104. One \emph{S. hookeriana} genotype did
      not interact with any galles and was removed from the network.
      The R code used to extract this 
      network follows:

@@

      Obtaining degree distributions from the binary interaction 
      network is straightforward. To do this, we simply divide the 
      total number of observed interaction partners for each 
      species (row or column sums) with the number of potential 
      interaction partners (number of column or rows). Degree 
      distributions calculated, we can then calculate the 
      probability of each interaction as the product of the 
      normalized degrees of the two species. For example, the 
      probability of an interaction between two species with 
      normalized degrees of 0.5 (each interacts with half of the 
      available partners) is 0.25. R code used to do this follows:

>>>>

      Barbour \emph{et al.} sampled 145 branches from 
      \emph{Salix hookeriana} of 26 genotypes. They recorded galls 
      made by four species of Cecidomyid midges on each branch. We 
      transformed these data to a binary genotype-galler network 
      matrix, where an entry $ij$ was 1 if galler $i$ was observed 
      on any branch of genotype $j$ and 0 otherwise. In total, this 
      network contained 75 realised galler-genotype interactions 
      out of a potential 104. One \emph{S. hookeriana} genotype did
      not interact with any gallers and was removed from the network.
      The R code used to extract this 
      network follows:

@@

      Obtaining degree distributions from the binary interaction 
      network is straightforward. To do this, we simply divide the 
      total number of observed interaction partners for each 
      species (row or column sums) with the number of potential 
      interaction partners (number of column or rows). Degree 
      distributions calculated, we can then calculate the 
      probability of each interaction as the product of the 
      normalised degrees of the two species. For example, the 
      probability of an interaction between two species with 
      normalised degrees of 0.5 (each interacts with half of the 
      available partners) is 0.25. R code used to do this follows:
